### 2017-01-02 Chapters/introduction.tex
Review hidde modifications of Introduction

Microorganisms, along with all living cells, are mainly constituted of polymers (DNA, RNA, proteins) consisting of many repeated subunits (nucleotides, amino acids).
The information about their sequences is stored in the form of genes physically located on the DNA.
Gene expression is the process by which this information is used in the synthesis of a functional final product (protein or RNA).
The gene expression machinery (itself constituted of RNA and proteins) synthesizes the gene products after binding to so-called promoters, target sequences on the DNA. [THIS IS NOT SUFFICIENTLY PRECISE: PROMOTERS IS ONLY FOR RNA, RBS FOR PROTEINS; GENERALIZE OR FOCUS ON TRANSCRIPTION]
In a given cell, there are roughly as many different target sequences as genes [REF MISSING], which ensures that not all products are synthesized at the same rate.
Furthermore, some of these products specifically bind some promoters and stimulate or repress promoter activity and hence gene expression.
These products are called transcription factors and allow, in addition to other mechanisms, the regulation of cell composition.

@@

Which allocation of resources is optimal for a living cell?
Systems capable of Darwinian evolution sustain themselves in the long run by \textit{fitting} to their environment~\cite{dawkins_selfish_1976}. [A BIT STRANGE THAT YOU ONLY USE ITALICS FOR KEY TERMS HERE AND NOT IN REST OF THESIS]
Living cells with the best \textit{fitness} are more likely to survive, replicate, and through long-term competition, eliminate their siblings.
The optimization criteria that quantitatively measure \textit{fitness} are called \textit{fitness factors}.
Whether they apply at the species, the population, the organism, or even the gene level has long been debated~\cite{dawkins_selfish_1976}.
An optimal resource allocation would be a gene expression scheme maximizing the fitness factors.
But since fitness factors have to take into account the ability to survive, reproduce, and compete with other organisms in a given (sometimes changing) environment, they are often context-dependent and highly difficult to identify.

For this reason, there is no consensus about what constitute the main fitness factors of microorganisms.
Competition for common resources seems to favor the maximization of offspring, in the sense that a replicator with more descendants will outnumber its competitors in the long term~\cite{dawkins_selfish_1976}.
It is unclear, however, how this general principle translates into specific features of microbial physiology.
For instance, the use of genome-scale metabolic network models has shown that metabolism maximizes the production either of biomass or available energy (ATP) depending on the environmental conditions~\cite{schuetz_systematic_2007}.
But we can also find other strategies for biomass production. [I CORRECTED THE ENGLISH, BUT DO NOT UNDERSTAND HOW THIS FITS IN WITH THE PREVIOUS PHRASE]
Microbes can either optimize their production yield (making the most of available nutrients at the expense of a lower growth rate) or their production rate (growing quickly while wasting part of the available nutrients), the latter being favored in fluctuating or poor [POOR, IS THAT TRUE? IT CONTRADICTS WHAT YOU SAY ON OVERFLOW METABOLISM BELOW... DATA OR THEORETICAL PREDICTION?] environments~\cite{frank_tradeoff_2010,maclean_tragedy_2008,schuster_maximization_2008}.
Overall, it seems that cell optimality drifts in a multidimensional space and involves making several trade-offs that strongly depend on the environmental context~\cite{schuetz_multidimensional_2012}.

Nevertheless, numerous studies have shown that considering growth rate maximization confers a good predictive power of microorganism physiology.
When cultivated in minimal medium with acetate or succinate, \textit{Escherichia coli} uptake rates are correctly predicted by assuming that the metabolic network operates in a mode that maximizes growth rate~\cite{edwards_silico_2001}.
This result is not general though, and depends on the carbon source and strain used~\cite{ibarra_escherichia_2002}.
But even in other situation, the metabolic networks evolve rapidly towards growth-rate maximization if a constant nutrient-providing environment is maintained~\cite{ibarra_escherichia_2002}.
The mutants obtained present modications in the regulation of the synthesis of metabolic enzymes~\cite{lewis_omic_2010}, indicating that not only the efficiency of the enzymes is affected, but also their abundance and thus the cellular composition.
Overall, with the currently available knowledge and its limitations (discussed in Section~\ref{chap:discussion}) [SEC. 1.4 or CHAP 4?], focusing on growth-rate maximization sounds like a rational choice to understand the growth strategies of microorganisms~\cite{molenaar_shifts_2009}.

@@

One of the first attempt to formalize the functioning of microbial physiology into elegant, fundamental laws was the discovery of Monod's law more than sixty years ago~\cite{monod_growth_1949}.
This empirical relationship states that the growth rate $\mu$ [\texttt{div h\textsuperscript{-1}}] of \textit{Escherichia coli} is a hyperbolic function of the concentration of the limiting nutrient $C$ [\texttt{mol L\textsuperscript{-1}}], such that
\begin{equation}
\label{eq:monod_law}
\mu = \mu_K \frac{C}{K_C + C},
\end{equation}
with $\mu_K$ and $K_C$ two constants depending on the quality of the nutrient (Fig.~\ref{fig:monod_law}).
It is remarkable that the growth rate, a parameter that depends on the use and production of thousands of proteins, can be so easily predicted by a simple relation.
What is even more remarkable is that this relation is rather universal.
Despite some adjustments (the Droop model being a well-known example~\cite{droop_thoughts_1973}), the relation holds for most microorganisms: the growth rate increases with the abundance of the limiting nutrient, up to a point beyond which they cannot grow any faster~\cite{koch_why_1988}.

@@

The production of every component of the cell is controlled by a complex network of regulatory interactions.
But an obvious constraint is that at steady state, the synthesis rate of all individual components must be proportional to the growth rate in order to compensate for growth dilution~\cite{monod_growth_1949}.
Many physiological parameters (like the mass of DNA, RNA and protein) are thus functions of the growth rate alone, regardless of the environmental conditions~\cite{schaechter_dependency_1958,bremer_modulation_1996}.
These so-called growth laws were carefully measured~\cite{bremer_modulation_1996} and are still used today in the quantitative understanding of growth control in microorganisms~\cite{ehrenberg_mediumdependent_2012}.
Recently, the topic was revitalized through the work of Scott \textit{et al}~\cite{scott_bacterial_2011}.
They focused on the ribosome concentration, a physiological parameter that was long known to vary linearly with the growth rate in microorganisms (Fig~\ref{fig:scott_rnaprot}).
By measuring it under different environmental perturbations of the protein synthesis machinery, they built a coarse-grained model describing proteome resource allocation~\cite{scott_emergence_2014}.
It has allowed to show that, whatever the details of the molecular implementation (differing between organisms), this growth law emerges from the underlying principles of robustness and optimization imposed by natural selection, especially growth-rate maximization, in all conditions~\cite{scott_emergence_2014}.

@@

The model will help us to establish actual resource allocation strategies that optimize biomass production during an environmental change.
However, it will not be able to tell us if microorganism do actually optimize such a criterion.
We therefore need to measure biomass accumulation and changes in resource allocation following a change in the environment.
How could one measure resource allocation during a growth transition?
In the light of the discussion in the previous section, tt requires to monitor the abundance of key macromolecules in living cells over time, while establishing an experimental set-up that allows to control the inherent variability of dynamical experimental studies of microbial growth.

@@

What makes mathematical modeling so useful in microbial growth studies?
Evolutionary biology is a good example of a field that has relied on mathematical modeling for a long time~\cite{servedio_not_2014}.
The large time and population scales at which evolutionary processes occur complicate experimental work, despite some attempts on organisms with a short generation time~\cite{elena_evolution_2003}. [YOU MAY WISH TO CITE A RECENT REVIEW ON EXPERIMENTAL EVOLUTION, WHICH IS NO LONGER RESTRICTED TO COLI]
Besides, microbiology is a field particularly prone to experimental study.
A growth curve as presented in Fig.~\ref{fig:growth_curve} can be made in a day, so the limitations of evolutionary biology should not apply to microbial growth studies.
Why care to mimic reality on a computer when we can just directly bend it to our will~\cite{hillis_why_1993}?
The last decades have strongly challenged this viewpoint: as knowledge and data on microbes accumulated, the need for a systemic understanding of biology was more and more pressing~\cite{alon_introduction_2006,kremling_systems_2013}.
[I HAVE NOT CORRECTED THE PARAGRAPH ABOVE, BECAUSE I DO NOT UNDERSTAND VERY WELL WHAT YOU MEAN AND HOW IT RELATES TO THE OPENING QUESTION]

Microbial physiology results from the interplay of thousands of chemical reactions that are not necessarily relevant in any given situation~\cite{schaechter_microbe_2006}.
These reactions occurs on short time scales [WHY SHORT? PROTEIN CONCENTRATION IS A SLOW VARIABLE? AS HALF6LIVES ARE OF THE ORDER OF 24H], and are controlled by several layers of regulatory mechanisms that can only be understood through evolutionary considerations.
As a consequence, even the simplest verbal hypothesis can resist direct empirical testing.
But abstracting away complexity is the purpose of mathematical models.
The overwhelming number of variables and the co-existence of several different time scales can be dealt with by choosing the correct framework.
When working on a model, microbial behavior is abstracted into a world of clearly stated rules, where logical reasoning can be applied~\cite{servedio_not_2014,mcgill_calm_2013}. [THIS IS AMBIGUOUS, AS ONE CAN REASON IN A "LOGICAL" WAY WITHOUT MODELS; MAYBE/ "where it is easier to spell out the logical consequences of the assumptions underlying the model"]
Predictions can be made, "unpacked" into our real world, and confronted with experimental testing.

Modeling has proven to be particularly helpful in unveiling how metabolic networks operate.
For an increasing number of microorganisms, we are now able to draw quasi-exhaustive maps of their metabolic reactions.
For instance, a much-used [NOT MOST RECENT] genome-scale reconstruction of \textit{E. coli} metabolism contains 1366 genes, 2251 metabolic reactions, and 1136 unique metabolites~\cite{orth_comprehensive_2011}.
The number of variables may seem overwhelming, and making sense of this information is not straightforward.
Which reactions are important, and in which environmental conditions?
Can we predict how perturbations will affect a given metabolic network?
Do fundamental regularities exist between different metabolic networks, from different species?

The complexity of the reconstructed metabolic networks does not impede their mathematical study.
Constraint-based modeling is a framework that abstracts away the unknown kinetics and represents the metabolic reactions by steady-state fluxes to which physico-chemical constraints can be applied, e.g., compartmentalization, mass conservation, molecular crowding, and thermodynamic directionality~\cite{ebrahim_cobrapy_2013}.
From a mathematical point of view, the model consists of a system of linear equations defining a space of admissible flux distributions that is further reduced by the above-mentioned constraints, which eliminate flux distributions that are unlikely to occur in an environmental condition of interest.
The solutions space is often further reduced by selecting the flux distributions optimizing a specified objective function, such as the growth rate of the cell.
This approach, called flux balance analysis (FBA)~\cite{orth_comprehensive_2011,palsson_systems_2011}, has been shown to correctly predict many behaviors of the metabolic network of \textit{E. coli}~\cite{varma_stoichiometric_1994,edwards_silico_2001}.
It has also proved capable of predicting its long-term adaptation through evolution of the network after a gene deletion~\cite{fong_metabolic_2004}.

More direct modeling approaches, in the form of large kinetic models, have also been helpful to understand growth-related processes.
Through the construction of a model of 47 differential equations and 193 parameters, Kotte \textit{et al} have shown how metabolic fluxes are sensed at different locations in central carbon metabolism, and are integrated in a global cellular response by the coupling of enzymatic and transcriptional regulation~\cite{kotte_bacterial_2010}.
Kinetic models of this type are sufficiently detailed to be used as an \textit{in silico} testbed to investigate specific molecular mechanisms and uncover their function in bringing about a cellular response~\cite{peskov_kinetic_2012}.
The most emblematic instance of this approach is probably the recent whole-cell model of \textit{Mycoplasma genitalium}~\cite{karr_whole-cell_2012}.
By aggregating all the available knowledge from more than 900 publications, Karr \textit{et al} constructed a dynamical model accounting for all the annotated gene functions of this pathogenic organism, and successfully used it to investigate unobserved molecular mechanisms and guide novel experimental analysis.
While such approach is not yet applicable to many organisms, it genuinely demonstrates how the increase in computational power could one day guide \textit{in silico} experimentation.

@@

The limitations of constraint-based and detailed kinetic models have motivated the construction of simpler, coarse-grained models.
The philosophy is quite different: instead of aggregating all available knowledge into a detailed model, the modeler is concerned about carefully filtering this information to keep the model as simple as possible.
The resulting models generally describe cellular functioning on a high level of abstraction, and are particularly valuable when looking for universal laws or principles~\cite{scott_bacterial_2011,scott_interdependence_2010,scott_emergence_2014}.
They can take the form of minimal core models that focus on a given aspect of growth, while still abstracting away the molecular details (see \textit{e.g.}, ~\cite{spiesser_size_2012}).
They can also be used as proof-of-concepts to submit verbal hypotheses to the logic and rigor of mathematical reasoning~\cite{servedio_not_2014}.
For instance, a simple proof-of-concept model was used to uncover the principles leading to overflow metabolism, a mechanism by which microorganisms switch to inefficient metabolic pathways when growing at high nutrient availability~\cite{molenaar_shifts_2009}.
This paradoxal and widespread phenomenon~\cite{dijken_kinetics_1993,vemuri_overflow_2006,mckeehan_glycolysis_1982,hsu_cancer_2008} was shown to be easily explained as a trade-off between the efficiency of a pathway and the cost of synthesis of its enzymes. [THIS IS NOT SUFFICIENTLY PRECISE, YOU NEED TO MAKE THE TRADE-OFF EXPLICIT]
Overall, these models have several advantages for the purpose of our study: they clearly state the underlying assumptions, and are sufficiently tractable to apply a variety of mathematical tools.

@@

Nevertheless, some questions cannot be solved at the population level~\cite{davey_flow_1996,bakshi_superresolution_2012,balaban_bacterial_2004}.
One example are questions about the internal structure of the cell~\cite{bakshi_superresolution_2012}.
Bakshi \textit{et al} used a combination of fluorescent labeling and superresolution imaging to localize the ribosomes, RNA polymerazes and DNA in living \textit{E. coli} cells~\cite{bakshi_superresolution_2012}.
They showed that despite what was previously thought, most of the translation occurs far from the DNA, on free mRNA molecules that migrate to ribosome-rich regions~\cite{bakshi_superresolution_2012}.
Another example concerns questions about single-cell variability~\cite{balaban_bacterial_2004,booth_stress_2002,sumner_phenotypic_2002}.
Through growth and imaging of single cells in a microfluidic device, Balaban \textit{et al} showed that a clonal bacterial population can profit from a preexisting heterogeneity to persist when challenged by the presence of an antibiotic, a short-term mechanism that does not involve any genetic mutation~\cite{balaban_bacterial_2004}.
In the long term, heterogeneity has also been shown to help subpopulations to resist lethal stresses, leaving them with enough time to adapt and conquer new ecological niches~\cite{booth_stress_2002,sumner_phenotypic_2002}.
In fact, cell heterogeneity seems so crucial for the fitness of microorganisms that diversity-generating mechanisms have been identified~\cite{true_yeast_2000,fraser_noise_2004,raser_control_2004}.

In addition to the level of measurement, the cultivation method plays a significant role in the kinds of question that an experiment can answer.
For a long time, batch growth conditions have been the preferred choice of most microbiologists~[citation?].
As illustrated in Fig.~\ref{fig:growth_curve}, the organism is inseminated in a closed-system and grows until the nutrient is depleted.
In a sense, such a condition is close to what microbes encounter in nature, where key nutrients are only available for a short time and quickly depleted~\cite{mcarthur_microbial_2006,menge_nitrogen_2012,hobbie_microbes_2013}.
The golden age of batch culturing was attained in the last decade with the democratization of culture in microplates. [I DON'T THINK THIS ASSERTION IS CORRECT FROM A HISTORICAL POINT OF VIEW, MICROPLATES JUST PARALLELIZED EXISTING PRACTICE. THIS EXISTING PRACTICE WAS NOT ALWAYS BAD PRACTICE, SINCE ESSENTIAL FOR MANY QUESTIONS, E.G. DIAUXIC GROWTH]
In parallel, dozens to hundreds of growth experiments can be performed each in less than one milliliter, while the optical density or the fluorescence of each culture is easily automatically monitored.
This has proven extremely helpful for screening purposes and the establishment of standard libraries of gene labeling and modification~\cite{baba_construction_2006,zaslaver_comprehensive_2006}.
Parallel cultivation has notably been exploited to construct roughly 4,000 single-cell knock-out mutants of \textit{Escherichia coli}, forming the Keio collection~\cite{baba_construction_2006}.
This mutant collection was intensively used during the last decade to unveil unknown gene functions and test genome-wide effects of gene deletions (as of 2009, more than 4 millions samples [WHAT DO YOU MEAN? THEY CAN'T HAVE SOLD 4 M COPIES OF THE COLLECTION...] had been distributed worldwide~\cite{yamamoto_update_2009}).
Microplates have also helped building a massive library of transcriptional fusions of the green fluorescent protein to each of about 2,000 different promoters in \textit{E.~coli}~\cite{zaslaver_comprehensive_2006}.
Interestingly, microplate batch growing conditions have also been used when applying the above constructions in the inference and analysis of gene regulatory networks~\cite{gerosa_dissecting_2013,berthoumieux_shared_2013,keren_promoters_2013,
ronen_assigning_2002,stefan_inference_2015}.
But the later use is hazardous, because the main drawback of the batch condition is that the culturing system is poorly controlled.
Changes of key chemical parameters (\textit{e.g.} pH, pO\textsubscript{2}) have been shown to occur during the whole growth curve~\cite{bekker_changes_2007}. 
At high density, metabolic by-products can accumulate in the medium and impede growth before nutrients are exhausted~\cite{ackerman_accumulation_1974,lenski_chemical_2002,luli_comparison_1990}.
This could be dealt with by focusing on the beginning of the culture, but this part has been shown to strongly depend on the preculture history~\cite{ng_damage_1962,dufrenne_effect_1997,shaw_effect_1967}, and one is never sure when an internal steady state has been reached~\cite{myers_culture_1944}. [NB THE FACT THAT CULTURE CONDITIONS CHANGE IS NOT NECESSARILY "HAZARDOUS", IF ALL MEASUREMENTS USED FOR THE INFERENCE PROCESS HAVE BEEN OBTAINED UNDER THE SAME CONDITIONS. THE CHANGE IN CONDITIONS IS ALSO A PERTURBATION OF THE NETWORK AND POSSIBLY INFORMATIVE...]

>>>>

Microorganisms, along with all living cells, are mainly constituted of polymers (DNA, RNA, proteins) consisting of many repeated subunits (nucleotides, amino acids).
The information about their sequences is stored in the form of genes physically located on the DNA.
Gene expression is the process by which this information is used in the synthesis of a functional final product (protein or RNA).
The gene expression machinery (itself constituted of RNA and proteins) synthesizes gene products after binding to target sequences either at the state of transcription (promoter on the DNA), or translation (ribosome binding site on the messaging RNA).
In a given cell, there are roughly as many different target sequences as genes~\cite{keseler_ecocyc:_2013}, which ensures that not all products are synthesized at the same rate.
Furthermore, some of these products specifically bind some promoters and stimulate or repress promoter activity and hence gene expression.
These products are called transcription factors and allow, in addition to other mechanisms, the regulation of cell composition.

@@

Which allocation of resources is optimal for a living cell?
Systems capable of Darwinian evolution sustain themselves in the long run by fitting to their environment~\cite{dawkins_selfish_1976}.
Living cells with the best fitness are more likely to survive, replicate, and through long-term competition, eliminate their siblings.
The optimization criteria that quantitatively measure fitness are called fitness factors.
Whether they apply at the species, the population, the organism, or even the gene level has long been debated~\cite{dawkins_selfish_1976}.
An optimal resource allocation would be a gene expression scheme maximizing the fitness factors.
But since fitness factors have to take into account the ability to survive, reproduce, and compete with other organisms in a given (sometimes changing) environment, they are often context-dependent and highly difficult to identify.

For this reason, there is no consensus about what constitute the main fitness factors of microorganisms.
Competition for common resources seems to favor the maximization of offspring, in the sense that a replicator with more descendants will outnumber its competitors in the long term~\cite{dawkins_selfish_1976}.
It is unclear, however, how this general principle translates into specific features of microbial physiology.
For instance, the use of genome-scale metabolic network models has shown that metabolism maximizes the production either of biomass or available energy (ATP) depending on the environmental conditions~\cite{schuetz_systematic_2007}.
Microbes can also either optimize their production yield (making the most of available nutrients at the expense of a lower growth rate) or their production rate (growing quickly while wasting part of the available nutrients), the latter being favored in fluctuating environments~\cite{frank_tradeoff_2010,maclean_tragedy_2008,schuster_maximization_2008}.
Overall, it seems that cell optimality drifts in a multidimensional space and involves making several trade-offs that strongly depend on the environmental context~\cite{schuetz_multidimensional_2012}.

Nevertheless, numerous studies have shown that considering growth rate maximization confers a good predictive power of microorganism physiology.
When cultivated in minimal medium with acetate or succinate, \textit{Escherichia coli} uptake rates are correctly predicted by assuming that the metabolic network operates in a mode that maximizes growth rate~\cite{edwards_silico_2001}.
This result is not general though, and depends on the carbon source and strain used~\cite{ibarra_escherichia_2002}.
But even in other situations, the metabolic networks evolve rapidly towards growth-rate maximization if a constant nutrient-providing environment is maintained~\cite{ibarra_escherichia_2002}.
The mutants obtained present modications in the regulation of the synthesis of metabolic enzymes~\cite{lewis_omic_2010}, indicating that not only the efficiency of the enzymes is affected, but also their abundance and thus the cellular composition.
Overall, with the currently available knowledge and its limitations (discussed in Chapter~\ref{chap:discussion}), focusing on growth-rate maximization sounds like a rational choice to understand the growth strategies of microorganisms~\cite{molenaar_shifts_2009}.

@@

One of the first attempt to formalize the functioning of microbial physiology into elegant, fundamental laws was the discovery of Monod's law more than sixty years ago~\cite{monod_growth_1949}.
This empirical relationship states that the growth rate $\mu$ [\texttt{div~h\textsuperscript{-1}}] of \textit{Escherichia coli} is a hyperbolic function of the concentration of the limiting nutrient $C$ [\texttt{mol~L\textsuperscript{-1}}], such that
\begin{equation}
\label{eq:monod_law}
\mu = \mu_K \frac{C}{K_C + C},
\end{equation}
with $\mu_K$ and $K_C$ two constants depending on the quality of the nutrient (Fig.~\ref{fig:monod_law}).
It is remarkable that the growth rate, a parameter that depends on the use and production of thousands of proteins, can be so easily predicted by a simple relation.
What is even more remarkable is that this relation is rather universal.
Despite some adjustments (the Droop model being a well-known example~\cite{droop_thoughts_1973}), the relation holds for most microorganisms: the growth rate increases with the abundance of the limiting nutrient, up to a point beyond which they cannot grow any faster~\cite{koch_why_1988}.

@@

The production of every component of the cell is controlled by a complex network of regulatory interactions.
But an obvious constraint is that at steady state, the synthesis rate of all individual components must be proportional to the growth rate in order to compensate for growth dilution~\cite{monod_growth_1949}.
Many physiological parameters (like the mass of DNA, RNA and protein) are thus functions of the growth rate alone, regardless of the environmental conditions~\cite{schaechter_dependency_1958,bremer_modulation_1996}.
These so-called growth laws were carefully measured~\cite{bremer_modulation_1996} and are still used today in the quantitative understanding of growth control in microorganisms~\cite{ehrenberg_mediumdependent_2012}.
Recently, the topic was revitalized through the work of Scott \textit{et al.}~\cite{scott_bacterial_2011}.
They focused on the ribosome concentration, a physiological parameter that was long known to vary linearly with the growth rate in microorganisms (Fig~\ref{fig:scott_rnaprot}).
By measuring it under different environmental perturbations of the protein synthesis machinery, they built a coarse-grained model describing proteome resource allocation~\cite{scott_emergence_2014}.
It has allowed to show that, whatever the details of the molecular implementation (differing between organisms), this growth law emerges from the underlying principles of robustness and optimization imposed by natural selection, especially growth-rate maximization, in all conditions~\cite{scott_emergence_2014}.

@@

The model will help us to establish actual resource allocation strategies that optimize biomass production during an environmental change.
However, it will not be able to tell us if microorganism do actually optimize such a criterion.
We therefore need to measure biomass accumulation and changes in resource allocation following a change in the environment.
How could one measure resource allocation during a growth transition?
In the light of the discussion in the previous section, it requires to monitor the abundance of key macromolecules in living cells over time, while establishing an experimental set-up that allows to control the inherent variability of dynamical experimental studies of microbial growth.

@@

What makes mathematical modeling so useful in microbial growth studies?
%Evolutionary biology is a good example of a field that has relied on mathematical modeling for a long time~\cite{servedio_not_2014}.
%The large time and population scales at which evolutionary processes occur complicate experimental work, despite several attempts on organisms with a short generation time~\cite{barrick_genome_2013,elena_evolution_2003,kassen_experimental_2002,schneider_dynamics_2004}.
%Besides, microbiology is a field particularly prone to experimental study.
%A growth curve as presented in Fig.~\ref{fig:growth_curve} can be made in a day, so the limitations of evolutionary biology should not apply to microbial growth studies.
%But as knowledge and experimental data on microbes accumulates, the need for a systemic understanding of biology is more and more pressing~\cite{alon_introduction_2006,kremling_systems_2013,hillis_why_1993}.
Microbial physiology results from the interplay of thousands of chemical reactions that are not necessarily relevant in any given situation~\cite{schaechter_microbe_2006}.
These reactions occurs on a wide range of time scales (shorter than 1~second for the metabolism, to more than 1~day for the degradation of stable proteins~\cite{schaechter_microbe_2006}), and are controlled by several layers of regulatory mechanisms that can only be understood through evolutionary considerations~\cite{dawkins_selfish_1976}.
As a consequence, even the simplest verbal hypothesis can resist direct empirical testing.
But abstracting away complexity is the purpose of mathematical models.
The overwhelming number of variables and the co-existence of several different time scales can be dealt with by choosing the correct framework.
When working on a model, microbial behavior is abstracted into a world of clearly stated rules, where it is easier to spell out the logical consequences of the underlying assumptions~\cite{servedio_not_2014,mcgill_calm_2013}.
Predictions can be made, "unpacked" into our real world, and confronted with experimental testing.

Modeling has proven to be particularly helpful in unveiling how metabolic networks operate.
For an increasing number of microorganisms, we are now able to draw quasi-exhaustive maps of their metabolic reactions.
For instance, a much-used genome-scale reconstruction of \textit{E. coli} metabolism contains 1366 genes, 2251 metabolic reactions, and 1136 unique metabolites~\cite{orth_comprehensive_2011}.
The number of variables may seem overwhelming, and making sense of this information is not straightforward.
Which reactions are important, and in which environmental conditions?
Can we predict how perturbations will affect a given metabolic network?
Do fundamental regularities exist between different metabolic networks, from different species?

The complexity of the reconstructed metabolic networks does not impede their mathematical study.
Constraint-based modeling is a framework that abstracts away the unknown kinetics and represents the metabolic reactions by steady-state fluxes to which physico-chemical constraints can be applied, e.g., compartmentalization, mass conservation, molecular crowding, and thermodynamic directionality~\cite{ebrahim_cobrapy_2013}.
From a mathematical point of view, the model consists of a system of linear equations defining a space of admissible flux distributions that is further reduced by the above-mentioned constraints, which eliminate flux distributions that are unlikely to occur in an environmental condition of interest.
The solution space is often further reduced by selecting the flux distributions optimizing a specified objective function, such as the growth rate of the cell.
This approach, called flux balance analysis (FBA)~\cite{orth_comprehensive_2011,palsson_systems_2011}, has been shown to correctly predict many behaviors of the metabolic network of \textit{E. coli}~\cite{varma_stoichiometric_1994,edwards_silico_2001}.
It has also proved capable of predicting its long-term adaptation through evolution of the network after a gene deletion~\cite{fong_metabolic_2004}.

More direct modeling approaches, in the form of large kinetic models, have also been helpful to understand growth-related processes.
Through the construction of a model of 47 differential equations and 193 parameters, Kotte \textit{et al.} have shown how metabolic fluxes are sensed at different locations in central carbon metabolism, and are integrated in a global cellular response by the coupling of enzymatic and transcriptional regulation~\cite{kotte_bacterial_2010}.
Kinetic models of this type are sufficiently detailed to be used as an \textit{in silico} testbed to investigate specific molecular mechanisms and uncover their function in bringing about a cellular response~\cite{peskov_kinetic_2012}.
The most emblematic instance of this approach is probably the recent whole-cell model of \textit{Mycoplasma genitalium}~\cite{karr_whole-cell_2012}.
By aggregating all the available knowledge from more than 900 publications, Karr \textit{et al.} constructed a dynamical model accounting for all the annotated gene functions of this pathogenic organism, and successfully used it to investigate unobserved molecular mechanisms and guide novel experimental analysis.
While such approach is not yet applicable to many organisms, it genuinely demonstrates how the increase in computational power could one day guide \textit{in silico} experimentation.

@@

The limitations of constraint-based and detailed kinetic models have motivated the construction of simpler, coarse-grained models.
The philosophy is quite different: instead of aggregating all available knowledge into a detailed model, the modeler is concerned about carefully filtering this information to keep the model as simple as possible.
The resulting models generally describe cellular functioning on a high level of abstraction, and are particularly valuable when looking for universal laws or principles~\cite{scott_bacterial_2011,scott_interdependence_2010,scott_emergence_2014}.
They can take the form of minimal core models that focus on a given aspect of growth, while still abstracting away the molecular details (see \textit{e.g.}, ~\cite{spiesser_size_2012}).
They can also be used as proof-of-concepts to submit verbal hypotheses to the logic and rigor of mathematical reasoning~\cite{servedio_not_2014}.
For instance, a simple proof-of-concept model was used to uncover the principles leading to overflow metabolism, a mechanism by which microorganisms switch to inefficient metabolic pathways when growing at high nutrient availability~\cite{molenaar_shifts_2009}.
This paradoxal and widespread phenomenon~\cite{dijken_kinetics_1993,vemuri_overflow_2006,mckeehan_glycolysis_1982,hsu_cancer_2008} was shown to be easily explained by the fact that high yield pathways also require the synthesis of more enzymes, revealing the occurrence of a cost-benefit trade-off producing the switch when nutrients are no longer the limiting factor.
Overall, these models have several advantages for the purpose of our study: they clearly state the underlying assumptions, and are sufficiently tractable to apply a variety of mathematical tools.

@@

Nevertheless, some questions cannot be solved at the population level~\cite{davey_flow_1996,bakshi_superresolution_2012,balaban_bacterial_2004}.
One example are questions about the internal structure of the cell~\cite{bakshi_superresolution_2012}.
Bakshi \textit{et al.} used a combination of fluorescent labeling and superresolution imaging to localize the ribosomes, RNA polymerazes and DNA in living \textit{E. coli} cells~\cite{bakshi_superresolution_2012}.
They showed that despite what was previously thought, most of the translation occurs far from the DNA, on free mRNA molecules that migrate to ribosome-rich regions~\cite{bakshi_superresolution_2012}.
Another example concerns questions about single-cell variability~\cite{balaban_bacterial_2004,booth_stress_2002,sumner_phenotypic_2002}.
Through growth and imaging of single cells in a microfluidic device, Balaban \textit{et al.} showed that a clonal bacterial population can profit from a preexisting heterogeneity to persist when challenged by the presence of an antibiotic, a short-term mechanism that does not involve any genetic mutation~\cite{balaban_bacterial_2004}.
In the long term, heterogeneity has also been shown to help subpopulations to resist lethal stresses, leaving them with enough time to adapt and conquer new ecological niches~\cite{booth_stress_2002,sumner_phenotypic_2002}.
In fact, cell heterogeneity seems so crucial for the fitness of microorganisms that diversity-generating mechanisms have been identified~\cite{true_yeast_2000,fraser_noise_2004,raser_control_2004}.

In addition to the level of measurement, the cultivation method plays a significant role in the kinds of question that an experiment can answer.
With the advent of molecular genetics in the 1970s and 1980s, batch growth conditions have been the preferred choice of most microbiologists~\cite{hoskisson_continuous_2005}.
As illustrated in Fig.~\ref{fig:growth_curve}, the organism is inseminated in a closed-system and grows until the nutrient is depleted.
In a sense, such a condition is close to what microbes encounter in nature, where key nutrients are only available for a short time and quickly depleted~\cite{mcarthur_microbial_2006,menge_nitrogen_2012,hobbie_microbes_2013}, and is essential to study many questions, \textit{e.g.} diauxic growth~\cite{kremling_understanding_2015}.
Currently, a strong advantage of batch culturing is the intense parallelization that can be attained using microplates.
Indeed, microplates allow to perform dozens to hundreds of growth experiments, each in less than one milliliter, while the optical density or the fluorescence of each culture is automatically monitored.
This has proven extremely helpful for screening purposes and the establishment of standard libraries of gene labeling and modification~\cite{baba_construction_2006,zaslaver_comprehensive_2006}.
Parallel cultivation has notably been exploited to construct roughly 4,000 single-cell knock-out mutants of \textit{Escherichia coli}, forming the Keio collection~\cite{baba_construction_2006}.
This mutant collection was intensively used during the last decade to unveil unknown gene functions and test genome-wide effects of gene deletions (as of 2009, more than 4 millions samples issued from this collection had been shared worldwide~\cite{yamamoto_update_2009}).
Microplates have also helped building a massive library of transcriptional fusions of the green fluorescent protein to each of about 2,000 different promoters in \textit{E.~coli}~\cite{zaslaver_comprehensive_2006}.
Interestingly, microplate batch growing conditions have also been used when applying the above constructions in the inference and analysis of gene regulatory networks~\cite{gerosa_dissecting_2013,berthoumieux_shared_2013,keren_promoters_2013,
ronen_assigning_2002,stefan_inference_2015}.
But the later use can be hazardous, because the main drawback of the batch condition is that the culturing system is poorly controlled.
Changes of key chemical parameters (\textit{e.g.} pH, pO\textsubscript{2}) have been shown to occur during the whole growth curve~\cite{bekker_changes_2007}. 
At high density, metabolic by-products can accumulate in the medium and impede growth before nutrients are exhausted~\cite{ackerman_accumulation_1974,lenski_chemical_2002,luli_comparison_1990}.
This could be dealt with by focusing on the beginning of the culture, but this part has been shown to strongly depend on the preculture history~\cite{ng_damage_1962,dufrenne_effect_1997,shaw_effect_1967}, and one is never sure when an internal steady state has been reached~\cite{myers_culture_1944}.
%[NB THE FACT THAT CULTURE CONDITIONS CHANGE IS NOT NECESSARILY "HAZARDOUS", IF ALL MEASUREMENTS USED FOR THE INFERENCE PROCESS HAVE BEEN OBTAINED UNDER THE SAME CONDITIONS. THE CHANGE IN CONDITIONS IS ALSO A PERTURBATION OF THE NETWORK AND POSSIBLY INFORMATIVE...]
% Nils: Indeed, but I need to make a point here in order to motivate why we used complicated culture.
